---
title: "Database Round Up Cocaine"
author: 'Palmer Lab: Bonnie Lin'
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# setwd("~/Dropbox (Palmer Lab)/Palmer Lab/Bonnie Lin/github/Olivier_U01Cocaine/QC")
# olivier_cocaine_genotyping <- flowcell_df %>% left_join(., WFU_OlivierCocaine_test_df[, c("cohort", "rfid")], by = "rfid") %>% subset(!is.na(cohort)) ## add source, consider reorganization source("~/Palmer\ Lab/Bonnie\ Lin/github/PalmerLab_genotyping/CREATE/EXTRACT_SAMPLEBARCODELIBRARY.R") # should work... might not bc it doesn't have dropbox in path
# save(WFU_OlivierCocaine_test_df, date_time_subject_df, rat_info_allcohort_xl_df, allcohorts2, olivier_spleens_df, olivier_cocaine_genotyping, file = "Olivier_cocaine_data.RData")
load(file = "Olivier_cocaine_data.RData")
```

## For Olivier George

Below, you will find the number of records that I have for your experiments, broken down by cohorts.


### \# of IDs from Wake Forest shipment sheets

```{r wfu-master, echo = F}
WFU_OlivierCocaine_test_df %>% select(cohort) %>% table()
```

### \# of subjects in raw data

These were extracted from the text files in *GWAS (1)/Cocaine/Cocaine GWAS*

```{r raw-data, echo = F}
date_time_subject_df %>% 
  distinct(labanimalid, cohort) %>% 
  select(cohort) %>% table()
```

### \# of subjects in excel data

These were extracted from the Excel sheets in *Olivier_George_U01/DATA Updated*

```{r xl-data, echo = F}
allcohorts2 %>% 
  mutate(cohort = paste0("C", as.character(parse_number(cohort)) %>% str_pad(2, "left", "0"))) %>% 
  distinct(cohort, labanimalid) %>% select(cohort) %>% table()
```

### \# of subjects with weight data

These were extracted from the Excel sheets in *Olivier_George_U01/Rat Information/Cocaine*

```{r weights, echo = F}
rat_info_allcohort_xl_df %>% distinct(cohort, rat) %>% 
  select(cohort) %>% table()
```

### \# of IDs from tissue shipments

Expected Spleens
```{r, echo = F}
olivier_spleens_df %>% 
  subset(experiment == "Cocaine") %>% 
  select(cohort) %>% table()
```

Extracted Spleens 
```{r, echo = F}
khai_tissueextraction_df %>%
  left_join(olivier_spleens_df[, c("rfid", "experiment", "cohort")], by = "rfid") %>% 
  rename("cohort_olivier" = "cohort_wfu") %>% 
  left_join(WFU_OlivierCocaine_test_df[, c("rfid", "cohort")]) %>% 
  subset(experiment == "Cocaine") %>% 
  select(cohort) %>% table()
```

### \# of subjects in genotyping pipeline

This is the number of animals we are currently genotyping. 

```{r genotyped, echo = F}
olivier_cocaine_genotyping %>% distinct(rfid, cohort) %>% 
  mutate(cohort = paste0("C", cohort)) %>% 
  select(cohort) %>% table()
```